Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-05-01 Latex Source/paper.tex

\documentclass[manuscript, screen, review]{acmart} %removing review removes the numbers on left side
% \documentclass was [sigconf]{acmart} changed to match with the given overleaf link
% \documentclass[sigconf]{acmart}

@@

\author{Shea Spalding}
\email{Shea1@colostate.edu} %update email 
\affiliation{%
  \institution{Colorado State University}
  \city{Fort Collins}
  \state{Colorado}
  \country{USA}
  \postcode{80521-1873} %chktex 8
}

@@

\section{Related Works}
While there is not necessarily a concrete answer for whether music or background noise is effective on cognitive function, there have been many
studies that attempt to determine the answer. 
The other studies attempted to search for this answer by focusing on word processing on a computer with the background music and the user's ability to formulate sentences~\cite{ransdell2001141}, or determining if background music helps users to keep their attention on their task at hand~\cite{kiss2021effect}. 
Similar to Kiss and Linnell~\cite{kiss2021effect}, Mathew ~\cite{mathew2022inherently} also examined how motivation and music were used hand-in-hand on ``a time-consuming task and task performance''. 
A different study done in 2010 again found similar results of music both being a hindrance and benefit~\cite{AudioDistractionsAshley}. 
According to Gonzalez and Aiello~\cite{Gonzalez_Aiello_2019}, the degree of cognitive function may be based on an individual's personality. 
Furnham et al., also determined this was based on personality in a study done between extraverts and introverts although ``no significant interactions were found''~\cite{distractingEffectsFurnham}.

@@

\section{Methodology}
After obtaining consent from all participants, they proceeded to take the typing test. The test presented lyrics from popular songs within a graphical user interface (GUI). 
The interface automatically calculated typing speed and accuracy in the program's backend, allowing participants to focus solely on completing the test.
Each participant completed the typing test under three conditions: music with lyrics, music without lyrics, and no music (silent condition).
Multiple levels of music intensity were utilized within each condition to assess varying degrees of distraction.
The GUI of the typing test was built with simplicity in mind. The starting window was pulled up so as not to confuse participants with the code as seen in Figure 1. The participants saw Figure 2 while the test is running, while Figure 3 is the signifier that the typing portion is finished.

@@

\subsection[short]{Participants}
Approximately eight participants were recruited from Colorado State University. NUMBER males and NUMBER females all in the age range of 18-99. There were no %chktex 8
restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
They have all previously either learned to type at primary school or through necessity.

@@

\subsection[short]{Procedure}
Each participant was instructed to read and then sign the consent form. While the consent form had the basis of what they would be doing, they were given more detail as to the instructions when they were ready to begin.
 %REWRITE THIS HERE
First they would take the short typing test three times to account for the three levels of music. 
They would then do a QBTest three times again for the music. The eye tracker is mounted around a laptop stand and the laptop is placed in between the stand so that the screen is behind the eyetracker.

>>>>

\documentclass[manuscript, screen, review]{acmart} %removing review removes the numbers on left side
% \documentclass[sigconf]{acmart}

@@

\author{Shea Spalding}
\email{Shea1@colostate.edu}
\affiliation{%
  \institution{Colorado State University}
  \city{Fort Collins}
  \state{Colorado}
  \country{USA}
  \postcode{80521-1873} %chktex 8
}

@@

\section{Related Works}
\subsection{Music While Working}
While there is not necessarily a concrete answer for whether music or background noise is effective on cognitive function, there have been many
studies that attempt to determine the answer. 
The other studies attempted to search for this answer by focusing on word processing on a computer with the background music and the user's ability to formulate sentences~\cite{ransdell2001141}, or determining if background music helps users to keep their attention on their task at hand~\cite{kiss2021effect}. 
Similar to Kiss and Linnell~\cite{kiss2021effect}, Mathew ~\cite{mathew2022inherently} also examined how motivation and music were used hand-in-hand on ``a time-consuming task and task performance''. 
A different study done in 2010 again found similar results of music both being a hindrance and benefit~\cite{AudioDistractionsAshley}. 
According to Gonzalez and Aiello~\cite{Gonzalez_Aiello_2019}, the degree of cognitive function may be based on an individual's personality. 
Furnham et al., also determined this was based on personality in a study done between extraverts and introverts although ``no significant interactions were found''~\cite{distractingEffectsFurnham}.

@@

\subsection{Eye Tracking and Quantified Behavioral Test}
% Citations about eye tracking and QBTest here

\section{Methodology}
After obtaining consent from all participants, they proceeded to take the typing test. The test presented lyrics from popular songs within a graphical user interface (GUI). 
The interface automatically calculated typing accuracy and the time the attempt took in the program's backend, allowing participants to focus solely on completing the test.
Each participant completed the typing test under three conditions: music with lyrics, music without lyrics, and no music (silent condition).
Multiple levels of music intensity were utilized within each condition to assess varying degrees of distraction.
The GUI of the typing test was built with simplicity in mind. The starting window was pulled up so as not to confuse participants with the code as seen in Figure 1. The participants saw Figure 2 while the test is running, while Figure 3 is the signifier that the typing portion is finished.

@@

\subsection[short]{Participants}
Tweleve participants were recruited from Colorado State University or Fort Collins, Colorado. NUMBER males and NUMBER females all in the age range of 18-99. There were no %chktex 8
restrictions in regards to their major as long as they were able to type on a keyboard with no tilt on the keys.
They have all previously either learned to type at primary school or through necessity.

@@

\subsection[short]{Procedure}
Each participant was instructed to read and then sign the consent form. While the consent form had the basis of what they would be doing, they were given more detail as to the instructions when they were ready to begin.
 %REWRITE THIS HERE
%First they would take the short typing test three times to account for the three levels of music. 
%They would then do a QBTest three times again for the music. 
%The eye tracker is mounted around a laptop stand and the laptop is placed in between the stand so that the screen is behind the eyetracker.
The two computers were set up side by side so that it would be easy for the participant to switch between the typing test and QBTest.
This setup also made it simple for the music component as the participants did each level together (e.g. the no music level was typing test 
then the QBTest) before moving on to the next level.
